### 2015-01-14 fundamentals/impl.tex
removed canonical

Interchangeability is accomplished by providing \glspl{API} that define canonical agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

>>>>

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.
